### 2015-07-25 paper/paper.Rmd
fixing package conflicts

world <- getMap(resolution = "low")
#library(plyr)
world.polys <- extractPolygons(world)
#detach("package:plyr")
```

@@

For each country, average scores on math and reading are calculated separately for boys and girls. These averages are differenced to compute the "gap" between boys and girls. Unadjusted t-statistics were calculated to determine the statistical significance of the difference. The results are plotted in the graphs below. Each dot corresponds to a difference between girls' and boys' scores, for each country. Color indicates statistical significance (blue in favor of boys, pink in favor of girls, and green means there was no significant difference).  For most countries it is roughly equal, but some countries have an imblance, for example, Malaysia has more girls tested than boys. The maps color the countries by the presence of a gender gap.

@@

```{r gendermath, fig.width=8, fig.height=12, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
#library(plyr)
student2012.sub <- student2012[, c(1, 12, 501, 541, 546, 634)]
student2012.sub.summary.gap <- summarise(group_by(student2012.sub, name), 
                  mathgap=mean(PV1MATH[ST04Q01=="Male"], na.rm=T)-
                          mean(PV1MATH[ST04Q01=="Female"], na.rm=T),
                  wmathgap=weighted.mean(PV1MATH[ST04Q01=="Male"], w=SENWGT_STU[ST04Q01=="Male"], na.rm=T)-
                          weighted.mean(PV1MATH[ST04Q01=="Female"], w=SENWGT_STU[ST04Q01=="Female"], na.rm=T),
                  mtest.stat = t.test(PV1MATH[ST04Q01=="Male"], PV1MATH[ST04Q01=="Female"])$statistic, 
                  mp.value = t.test(PV1MATH[ST04Q01=="Male"], PV1MATH[ST04Q01=="Female"])$p.value,
                  readgap=mean(PV1READ[ST04Q01=="Male"], na.rm=T)-mean(PV1READ[ST04Q01=="Female"], na.rm=T),
                  rtest.stat = t.test(PV1READ[ST04Q01=="Male"], PV1READ[ST04Q01=="Female"])$statistic, 
                  rp.value = t.test(PV1READ[ST04Q01=="Male"], PV1READ[ST04Q01=="Female"])$p.value,
                  sciencegap=mean(PV1SCIE[ST04Q01=="Male"], na.rm=T)-mean(PV1SCIE[ST04Q01=="Female"], na.rm=T),
                  stest.stat = t.test(PV1SCIE[ST04Q01=="Male"], PV1SCIE[ST04Q01=="Female"])$statistic, 
                  sp.value = t.test(PV1SCIE[ST04Q01=="Male"], PV1SCIE[ST04Q01=="Female"])$p.value,         
                  minmale=min(PV1MATH[ST04Q01=="Male"], na.rm=T), 
                  minfemale=min(PV1MATH[ST04Q01=="Female"], na.rm=T), 
                  maxmale=max(PV1MATH[ST04Q01=="Male"], na.rm=T), 
                  maxfemale=max(PV1MATH[ST04Q01=="Female"], na.rm=T), 
                  propmale=length(PV1MATH[ST04Q01=="Male"])/length(PV1MATH), 
                  propfemale=length(PV1MATH[ST04Q01=="Female"])/length(PV1MATH))
#qplot(mathgap, wmathgap, data=student2012.sub.summary.gap, xlab="Mean", ylab="Weighted Mean",
#      xlim=c(-30,30), ylim=c(-30,30)) + geom_abline(slope=1) + theme(aspect.ratio=1)
student2012.sub.summary.gap$msig <- ifelse(student2012.sub.summary.gap$mp.value>0.05, "none", TRUE)
student2012.sub.summary.gap$msig[student2012.sub.summary.gap$msig==TRUE&student2012.sub.summary.gap$mtest.stat>0] <- "male"
student2012.sub.summary.gap$msig[student2012.sub.summary.gap$msig==TRUE&student2012.sub.summary.gap$mtest.stat<0] <- "female"
cifn <- function(d, i) {
  x <- d[i,]
  ci <- mean(x$PV1MATH[x$ST04Q01=="Male"], na.rm=T)-
     mean(x$PV1MATH[x$ST04Q01=="Female"], na.rm=T)
  ci
}
bootfn <- function(d) {
  r <- boot(d, statistic=cifn, R=1000)
  l <- sort(r$t)[25]
  u <- sort(r$t)[975]
  ci <- c(l, u)
  return(ci)
}
#ddply(student2012.sub, .(name), bootfn)
#results <- boot(data=aus, statistic=cifn, R=1000)
student2012.sub.summary.gap.boot <- ddply(student2012.sub, .(name), bootfn)
colnames(student2012.sub.summary.gap.boot)[2:3] <- c("ml", "mu")
student2012.sub.summary.gap <- merge(student2012.sub.summary.gap, student2012.sub.summary.gap.boot)
student2012.sub.summary.gap$name <- factor(student2012.sub.summary.gap$name, 
      levels=student2012.sub.summary.gap$name[order(student2012.sub.summary.gap$mathgap)])
qplot(name, mathgap, data=student2012.sub.summary.gap, color=msig, size=I(3)) + 
  geom_segment(aes(x=name, xend=name, y=ml, yend=mu)) +
  xlab("") +  
  scale_colour_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
  scale_y_continuous("Math Score Gap", breaks=seq(-45, 45, 5), limits=c(-45, 45)) + 
   geom_hline(yintercept=0, colour="grey80") + coord_flip() + theme_bw() + theme(legend.position="bottom")
```

@@

```{r genderead, fig.width=8, fig.height=12, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
student2012.sub.summary.gap$rsig <- ifelse(student2012.sub.summary.gap$rp.value>0.05, "none", TRUE)
student2012.sub.summary.gap$rsig[student2012.sub.summary.gap$rsig==TRUE&student2012.sub.summary.gap$rtest.stat>0] <- "male"
student2012.sub.summary.gap$rsig[student2012.sub.summary.gap$rsig==TRUE&student2012.sub.summary.gap$rtest.stat<0] <- "female"
cifn <- function(d, i) {
  x <- d[i,]
  ci <- mean(x$PV1READ[x$ST04Q01=="Male"], na.rm=T)-
     mean(x$PV1READ[x$ST04Q01=="Female"], na.rm=T)
  ci
}
bootfn <- function(d) {
  r <- boot(d, statistic=cifn, R=1000)
  l <- sort(r$t)[25]
  u <- sort(r$t)[975]
  ci <- c(l, u)
  return(ci)
}
#ddply(student2012.sub, .(name), bootfn)
#results <- boot(data=aus, statistic=cifn, R=1000)
student2012.sub.summary.gap.boot <- ddply(student2012.sub, .(name), bootfn)
colnames(student2012.sub.summary.gap.boot)[2:3] <- c("rl", "ru")
student2012.sub.summary.gap <- merge(student2012.sub.summary.gap, student2012.sub.summary.gap.boot)
student2012.sub.summary.gap$name <- factor(student2012.sub.summary.gap$name, 
      levels=student2012.sub.summary.gap$name[order(student2012.sub.summary.gap$readgap)])
qplot(name, readgap, data=student2012.sub.summary.gap, color=rsig, size=I(3)) + 
  geom_segment(aes(x=name, xend=name, y=rl, yend=ru)) +
  xlab("") +
  scale_colour_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
  scale_y_continuous("Reading Score Gap") + 
   geom_hline(yintercept=0, colour="grey80") + coord_flip() + theme_bw() + theme(legend.position="bottom")
#ggsave("genderreadgap.pdf", width=5, height=8)
#student2012.sub.summary.gap$ssig <- ifelse(student2012.sub.summary.gap$sp.value>0.05, "none", TRUE)
#student2012.sub.summary.gap$ssig[student2012.sub.summary.gap$ssig==TRUE&student2012.sub.summary.gap$stest.stat>0] <- "male"
#student2012.sub.summary.gap$ssig[student2012.sub.summary.gap$ssig==TRUE&student2012.sub.summary.gap$stest.stat<0] <- "female"
#student2012.sub.summary.gap$name <- factor(student2012.sub.summary.gap$name, 
#      levels=student2012.sub.summary.gap$name[order(student2012.sub.summary.gap$sciencegap)])
#qplot(name, sciencegap, data=student2012.sub.summary.gap, size=propmale, color=ssig) + 
#  xlab("") +
#  scale_colour_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
#  scale_y_continuous("Science Score Gap") + 
#  scale_size("Prop male") +
#   geom_hline(yintercept=0, colour="grey80") + coord_flip() + theme_bw()
```

@@

```{r age, cache=FALSE, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
#library(dplyr)
detach("package:plyr")
student2012.sub <- student2012[, c(1, 6, 12, 14, 501, 541, 546, 634)]
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  math4 = mean(PV1MATH[ST06Q01 == 4], na.rm = T), 
                  math5 = mean(PV1MATH[ST06Q01 == 5], na.rm = T), 
                  math6 = mean(PV1MATH[ST06Q01 == 6], na.rm = T), 
                  math7 = mean(PV1MATH[ST06Q01 == 7], na.rm = T), 
                  math8 = mean(PV1MATH[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
student2012.sub.agemedian <- summarise(group_by(student2012.sub, name), medianstart = median(ST06Q01, na.rm=T))
orderedbymedianage <- student2012.sub.agemedian$name[order(student2012.sub.agemedian$medianstart)]
student2012.sub.age.m.median <- left_join(student2012.sub.age.m, student2012.sub.agemedian, by="name")
student2012.sub.age.m.median$medianstart <- factor(student2012.sub.age.m.median$medianstart)
student2012.sub.age.m.median$name <- factor(student2012.sub.age.m.median$name, levels=orderedbymedianage)
qplot(variable, value, data=student2012.sub.age.m.median, xlab="Age at start", ylab="Math score", 
      geom=c("point","smooth"), se=F, group=name, colour=medianstart) + 
 facet_wrap(~name, ncol=8) + theme_bw() + theme(legend.position="none")
# ggsave("school-start.pdf", width=14, height=14)
#student2012.sub.age <- summarise(group_by(student2012.sub, name), 
#                  read4 = mean(PV1READ[ST06Q01 == 4], na.rm = T), 
#                  read5 = mean(PV1READ[ST06Q01 == 5], na.rm = T), 
#                  read6 = mean(PV1READ[ST06Q01 == 6], na.rm = T), 
#                  read7 = mean(PV1READ[ST06Q01 == 7], na.rm = T), 
#                  read8 = mean(PV1READ[ST06Q01 >  7], na.rm = T))
#student2012.sub.age.m <- melt(student2012.sub.age)
#student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
#student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
#qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Reading Score", 
#      geom=c("point","smooth"), se=F, group=name) + 
# facet_wrap(~name, ncol=8) + theme_bw() 
#student2012.sub.age <- summarise(group_by(student2012.sub, name), 
#                  scie4 = mean(PV1SCIE[ST06Q01 == 4], na.rm = T), 
#                  scie5 = mean(PV1SCIE[ST06Q01 == 5], na.rm = T), 
#                  scie6 = mean(PV1SCIE[ST06Q01 == 6], na.rm = T), 
#                  scie7 = mean(PV1SCIE[ST06Q01 == 7], na.rm = T), 
#                  scie8 = mean(PV1SCIE[ST06Q01 >  7], na.rm = T))
#student2012.sub.age.m <- melt(student2012.sub.age)
#student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
#student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
#qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Science Score", 
#      geom=c("point","smooth"), se=F, group=name) + 
# facet_wrap(~name, ncol=8) + theme_bw() 
```

>>>>

world <- getMap(resolution = "low")
#library(plyr)
world.polys <- extractPolygons(world)
detach("package:plyr")
```

@@

For each country, average scores on math and reading are calculated separately for boys and girls. These averages are differenced to compute the "gap" between boys and girls. To gauge the statistical significance of the difference, t-statistics and bootstrap confidence intervals were calculated. The results are plotted in the graphs below. Each dot corresponds to a difference between girls' and boys' scores, for each country, with lines giving the confidence interval. Wider intervals indicate less data support the statistics. Color indicates statistical significance (blue in favor of boys, pink in favor of girls, and green means there was no significant difference). The maps color the countries by the presence (or absence) of a gender gap.

@@

```{r gendermath, fig.width=8, fig.height=12, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
#library(plyr)
student2012.sub <- student2012[, c(1, 12, 501, 541, 546, 634)]
student2012.sub.summary.gap <- summarise(group_by(student2012.sub, name), 
                  mathgap=mean(PV1MATH[ST04Q01=="Male"], na.rm=T)-
                          mean(PV1MATH[ST04Q01=="Female"], na.rm=T),
                  wmathgap=weighted.mean(PV1MATH[ST04Q01=="Male"], w=SENWGT_STU[ST04Q01=="Male"], na.rm=T)-
                          weighted.mean(PV1MATH[ST04Q01=="Female"], w=SENWGT_STU[ST04Q01=="Female"], na.rm=T),
                  mtest.stat = t.test(PV1MATH[ST04Q01=="Male"], PV1MATH[ST04Q01=="Female"])$statistic, 
                  mp.value = t.test(PV1MATH[ST04Q01=="Male"], PV1MATH[ST04Q01=="Female"])$p.value,
                  readgap=mean(PV1READ[ST04Q01=="Male"], na.rm=T)-mean(PV1READ[ST04Q01=="Female"], na.rm=T),
                  rtest.stat = t.test(PV1READ[ST04Q01=="Male"], PV1READ[ST04Q01=="Female"])$statistic, 
                  rp.value = t.test(PV1READ[ST04Q01=="Male"], PV1READ[ST04Q01=="Female"])$p.value,
                  sciencegap=mean(PV1SCIE[ST04Q01=="Male"], na.rm=T)-mean(PV1SCIE[ST04Q01=="Female"], na.rm=T),
                  stest.stat = t.test(PV1SCIE[ST04Q01=="Male"], PV1SCIE[ST04Q01=="Female"])$statistic, 
                  sp.value = t.test(PV1SCIE[ST04Q01=="Male"], PV1SCIE[ST04Q01=="Female"])$p.value,         
                  minmale=min(PV1MATH[ST04Q01=="Male"], na.rm=T), 
                  minfemale=min(PV1MATH[ST04Q01=="Female"], na.rm=T), 
                  maxmale=max(PV1MATH[ST04Q01=="Male"], na.rm=T), 
                  maxfemale=max(PV1MATH[ST04Q01=="Female"], na.rm=T), 
                  propmale=length(PV1MATH[ST04Q01=="Male"])/length(PV1MATH), 
                  propfemale=length(PV1MATH[ST04Q01=="Female"])/length(PV1MATH))
#qplot(mathgap, wmathgap, data=student2012.sub.summary.gap, xlab="Mean", ylab="Weighted Mean",
#      xlim=c(-30,30), ylim=c(-30,30)) + geom_abline(slope=1) + theme(aspect.ratio=1)
student2012.sub.summary.gap$msig <- ifelse(student2012.sub.summary.gap$mp.value>0.05, "none", TRUE)
student2012.sub.summary.gap$msig[student2012.sub.summary.gap$msig==TRUE&student2012.sub.summary.gap$mtest.stat>0] <- "male"
student2012.sub.summary.gap$msig[student2012.sub.summary.gap$msig==TRUE&student2012.sub.summary.gap$mtest.stat<0] <- "female"
cifn <- function(d, i) {
  x <- d[i,]
  ci <- mean(x$PV1MATH[x$ST04Q01=="Male"], na.rm=T)-
     mean(x$PV1MATH[x$ST04Q01=="Female"], na.rm=T)
  ci
}
bootfn <- function(d) {
  r <- boot(d, statistic=cifn, R=1000)
  l <- sort(r$t)[25]
  u <- sort(r$t)[975]
  ci <- c(l, u)
  return(ci)
}
#ddply(student2012.sub, .(name), bootfn)
#results <- boot(data=aus, statistic=cifn, R=1000)
library(plyr)
student2012.sub.summary.gap.boot <- ddply(student2012.sub, .(name), bootfn)
detach("package:plyr")
colnames(student2012.sub.summary.gap.boot)[2:3] <- c("ml", "mu")
student2012.sub.summary.gap <- merge(student2012.sub.summary.gap, student2012.sub.summary.gap.boot)
student2012.sub.summary.gap$name <- factor(student2012.sub.summary.gap$name, 
      levels=student2012.sub.summary.gap$name[order(student2012.sub.summary.gap$mathgap)])
qplot(name, mathgap, data=student2012.sub.summary.gap, color=msig, size=I(3)) + 
  geom_segment(aes(x=name, xend=name, y=ml, yend=mu)) +
  xlab("") +  
  scale_colour_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
  scale_y_continuous("Math Score Gap", breaks=seq(-45, 45, 5), limits=c(-45, 45)) + 
   geom_hline(yintercept=0, colour="grey80") + coord_flip() + theme_bw() + theme(legend.position="bottom")
```

@@

```{r genderead, fig.width=8, fig.height=12, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
student2012.sub.summary.gap$rsig <- ifelse(student2012.sub.summary.gap$rp.value>0.05, "none", TRUE)
student2012.sub.summary.gap$rsig[student2012.sub.summary.gap$rsig==TRUE&student2012.sub.summary.gap$rtest.stat>0] <- "male"
student2012.sub.summary.gap$rsig[student2012.sub.summary.gap$rsig==TRUE&student2012.sub.summary.gap$rtest.stat<0] <- "female"
cifn <- function(d, i) {
  x <- d[i,]
  ci <- mean(x$PV1READ[x$ST04Q01=="Male"], na.rm=T)-
     mean(x$PV1READ[x$ST04Q01=="Female"], na.rm=T)
  ci
}
bootfn <- function(d) {
  r <- boot(d, statistic=cifn, R=1000)
  l <- sort(r$t)[25]
  u <- sort(r$t)[975]
  ci <- c(l, u)
  return(ci)
}
#ddply(student2012.sub, .(name), bootfn)
#results <- boot(data=aus, statistic=cifn, R=1000)
library(plyr)
student2012.sub.summary.gap.boot <- ddply(student2012.sub, .(name), bootfn)
detach("package:plyr")
colnames(student2012.sub.summary.gap.boot)[2:3] <- c("rl", "ru")
student2012.sub.summary.gap <- merge(student2012.sub.summary.gap, student2012.sub.summary.gap.boot)
student2012.sub.summary.gap$name <- factor(student2012.sub.summary.gap$name, 
      levels=student2012.sub.summary.gap$name[order(student2012.sub.summary.gap$readgap)])
qplot(name, readgap, data=student2012.sub.summary.gap, color=rsig, size=I(3)) + 
  geom_segment(aes(x=name, xend=name, y=rl, yend=ru)) +
  xlab("") +
  scale_colour_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
  scale_y_continuous("Reading Score Gap") + 
   geom_hline(yintercept=0, colour="grey80") + coord_flip() + theme_bw() + theme(legend.position="bottom")
#ggsave("genderreadgap.pdf", width=5, height=8)
#student2012.sub.summary.gap$ssig <- ifelse(student2012.sub.summary.gap$sp.value>0.05, "none", TRUE)
#student2012.sub.summary.gap$ssig[student2012.sub.summary.gap$ssig==TRUE&student2012.sub.summary.gap$stest.stat>0] <- "male"
#student2012.sub.summary.gap$ssig[student2012.sub.summary.gap$ssig==TRUE&student2012.sub.summary.gap$stest.stat<0] <- "female"
#student2012.sub.summary.gap$name <- factor(student2012.sub.summary.gap$name, 
#      levels=student2012.sub.summary.gap$name[order(student2012.sub.summary.gap$sciencegap)])
#qplot(name, sciencegap, data=student2012.sub.summary.gap, size=propmale, color=ssig) + 
#  xlab("") +
#  scale_colour_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
#  scale_y_continuous("Science Score Gap") + 
#  scale_size("Prop male") +
#   geom_hline(yintercept=0, colour="grey80") + coord_flip() + theme_bw()
```

@@

```{r age, cache=FALSE, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
#library(dplyr)
#detach("package:plyr")
student2012.sub <- student2012[, c(1, 6, 12, 14, 501, 541, 546, 634)]
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  math4 = mean(PV1MATH[ST06Q01 == 4], na.rm = T), 
                  math5 = mean(PV1MATH[ST06Q01 == 5], na.rm = T), 
                  math6 = mean(PV1MATH[ST06Q01 == 6], na.rm = T), 
                  math7 = mean(PV1MATH[ST06Q01 == 7], na.rm = T), 
                  math8 = mean(PV1MATH[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
student2012.sub.agemedian <- summarise(group_by(student2012.sub, name), medianstart = median(ST06Q01, na.rm=T))
orderedbymedianage <- student2012.sub.agemedian$name[order(student2012.sub.agemedian$medianstart)]
student2012.sub.age.m.median <- left_join(student2012.sub.age.m, student2012.sub.agemedian, by="name")
student2012.sub.age.m.median$medianstart <- factor(student2012.sub.age.m.median$medianstart)
student2012.sub.age.m.median$name <- factor(student2012.sub.age.m.median$name, levels=orderedbymedianage)
qplot(variable, value, data=student2012.sub.age.m.median, xlab="Age at start", ylab="Math score", 
      geom=c("point","smooth"), se=F, group=name, colour=medianstart) + 
 facet_wrap(~name, ncol=8) + theme_bw() + theme(legend.position="none")
# ggsave("school-start.pdf", width=14, height=14)
#student2012.sub.age <- summarise(group_by(student2012.sub, name), 
#                  read4 = mean(PV1READ[ST06Q01 == 4], na.rm = T), 
#                  read5 = mean(PV1READ[ST06Q01 == 5], na.rm = T), 
#                  read6 = mean(PV1READ[ST06Q01 == 6], na.rm = T), 
#                  read7 = mean(PV1READ[ST06Q01 == 7], na.rm = T), 
#                  read8 = mean(PV1READ[ST06Q01 >  7], na.rm = T))
#student2012.sub.age.m <- melt(student2012.sub.age)
#student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
#student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
#qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Reading Score", 
#      geom=c("point","smooth"), se=F, group=name) + 
# facet_wrap(~name, ncol=8) + theme_bw() 
#student2012.sub.age <- summarise(group_by(student2012.sub, name), 
#                  scie4 = mean(PV1SCIE[ST06Q01 == 4], na.rm = T), 
#                  scie5 = mean(PV1SCIE[ST06Q01 == 5], na.rm = T), 
#                  scie6 = mean(PV1SCIE[ST06Q01 == 6], na.rm = T), 
#                  scie7 = mean(PV1SCIE[ST06Q01 == 7], na.rm = T), 
#                  scie8 = mean(PV1SCIE[ST06Q01 >  7], na.rm = T))
#student2012.sub.age.m <- melt(student2012.sub.age)
#student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
#student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
#qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Science Score", 
#      geom=c("point","smooth"), se=F, group=name) + 
# facet_wrap(~name, ncol=8) + theme_bw() 
```
